\emph{icepack}: a new glacier flow modeling package in Python, version 1.0

### 2021-04-06 icepack.tex
Name spellings

\Author[1]{Daniel R}{Shapero}
\Author[2]{Jessica A}{Badgeley}
\Author[2]{Andrew O}{Hoffmann}
\Author[1]{Ian R}{Joughin}

@@

\runningauthor{Shapero, Badgeley, Hoffmann, Joughin}

@@

\textit{Financial support}.
DS was supported by US National Science Foundation grant \#1835321 and National Aeronautics and Space Administration grant \#80NSSC20K0954.
JB was supported by NSF grant \#1256082.
AH was supported by NASA grant \#80NSSC20K1627.
IJ was supported by NSF grants \#1835321 and \#1643285.

>>>>

\Author[1]{Daniel R}{Shapero}
\Author[2]{Jessica A}{Badgeley}
\Author[2]{Andrew O}{Hoffman}
\Author[1]{Ian R}{Joughin}

@@

\runningauthor{Shapero, Badgeley, Hoffman, Joughin}

@@

\textit{Financial support}.
DRS was supported by US National Science Foundation grant \#1835321 and National Aeronautics and Space Administration grant \#80NSSC20K0954.
JAB was supported by NSF grant \#1256082.
AOH was supported by NASA grant \#80NSSC20K1627.
IRJ was supported by NSF grants \#1835321 and \#1643285.
